### 2014-03-12 src/analysis.Rnw
update

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames

o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', subset(o.stats.sel.xp, grepl('^rr[.]', operator))$operator)
r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', subset(r.stats.sel.xp, grepl('^rr[.]', operator))$operator)

o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(o.stats.sel.xp, grepl('^r[.]', operator))$operator)
r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(r.stats.sel.xp, grepl('^r[.]', operator))$operator)

o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(o.stats.sel.xp, grepl('^rc[.]', operator))$operator)
r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(r.stats.sel.xp, grepl('^rc[.]', operator))$operator)

@
\subsubsection{x\% selection}
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.sample, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.sample, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.round, caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.round, caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.ceil, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.ceil, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xselceil}
\end{table*}

\section{Analysis}
\label{sec:analysis}

Our results for x\% sampling over program elements are given in Table~\ref{tbl:xselsample}. The result of
its variation, using \textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result of using \textit{ceil(sample)}
is given in Table~\ref{tbl:xselceil}.

First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
This provided us with the relative number of each mutation operators, that are produced, and also the general number of
mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}. This suggests that the operators
are distributed in the following order: \pitnvmc, \pitnc, \pitrc, \pitdc, \pitrv, \pitic, \pitcc, \pitemv, \pitvmc, \pitm,
\pitcb, \piti, \pitri, \pitrs, \pites, \pitin. We use this information later for n-selective mutation.

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Sampling Criteria}

>>>>

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
o.stats.sel.xp$scope <- NA
r.stats.sel.xp$scope <- NA
o.stats.sel.xp$sampling <- NA
r.stats.sel.xp$sampling <- NA

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  return(x)
}

o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))

o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)

o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))

o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)

o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))

o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)

@
\subsubsection{x\% selection}
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xselceil}
\end{table*}

\section{Analysis}
\label{sec:analysis}
Our results for x\% sampling over program elements are given
in Table~\ref{tbl:xselsample}. The result of its variation, using
\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criterias for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

\subsection{Sampling Criteria}
